Verifying Demonstrations

### 2018-10-31 paper/privacy-properties.tex
restores privacy properties from before conflict resolution

\sonja{start of older thoughts}
Difference to e-voting:
physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
\begin{enumerate*}
\item they participate in the protocol,
\item they use the protest identifier (cause) for which the count is done,
\item they meet the eligibility criteria, and
\item they receive enough proof shares,
\item that are uploaded to the ledger.
\end{enumerate*}
Thus one could participate in a protest and be counted even when physically 
present at a counter-protest if the two protests are co-located and the 
participant chooses the corresponding cause/identifier of the original protest.

Given that all conditions for being counted in a protest are met, individual 
verifiability implies a receipt \daniel{no, I know my proof is included in 
 block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
 sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
 to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
 hence receipt-freeness} because being counted implies support for a cause. 
This also means that besides physical force, coercion can happen by forcing the 
participate to show a receipt. \daniel{The only receipt we have is the private 
 key of the protester, with that key the adversary can compute \(\pid = 
   \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
We thus have to decide between individual verifiability and the privacy 
properties for e-voting or define privacy properties suitable for the scenario. 
The ultimate privacy requirement is thus stronger here: in contrast to voting, 
where it is the content of the vote itself that needs to be unlinkable to the 
voter, here the fact of having cast a vote at all needs to be unlinkable.

The privacy properties we need in this context are the following:
\begin{description}
 \item[Involuntary participant unlinkability:] \daniel{the name has a 
     double-negative ring to me} unless the participant discloses the receipt 
   (by revealing her identity), there is no link between the protest data on 
   the ledger and the identity of the participant.

 \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
     too of course} unless the witness discloses the receipt (by revealing her 
   identity), there is no link between the protest data on the ledger and the 
   identity of the witness.
\end{description}

In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

As a consequence, this leaves us with with what would correspond to vote privacy.
In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
\sonja{end older thoughts}
Moreover, any temporary identifiers such as pseudonyms may only be
reused when strictly necessary for the fulfillment of verifiability
properties listed in \label{verifiability-properties} to prevent
inference on long-term identities by repeated samples and side information.

>>>>

% \sonja{start of older thoughts}
% Difference to e-voting:
% physical presence means support for a cause if there is one protest. If there is a counterprotest, physical presence with that group means support for the counterprotest. In our system, it gets more ambiguous as the participants are counted if all of the following is true
% \begin{enumerate*}
% \item they participate in the protocol,
% \item they use the protest identifier (cause) for which the count is done,
% \item they meet the eligibility criteria, and
% \item they receive enough proof shares,
% \item that are uploaded to the ledger.
% \end{enumerate*}
% Thus one could participate in a protest and be counted even when physically 
% present at a counter-protest if the two protests are co-located and the 
% participant chooses the corresponding cause/identifier of the original protest.

% Given that all conditions for being counted in a protest are met, individual 
% verifiability implies a receipt \daniel{no, I know my proof is included in 
%  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
%  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
%  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
%  hence receipt-freeness} because being counted implies support for a cause. 
% This also means that besides physical force, coercion can happen by forcing the 
% participate to show a receipt. \daniel{The only receipt we have is the private 
%  key of the protester, with that key the adversary can compute \(\pid = 
%    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
% We thus have to decide between individual verifiability and the privacy 
% properties for e-voting or define privacy properties suitable for the scenario. 
% The ultimate privacy requirement is thus stronger here: in contrast to voting, 
% where it is the content of the vote itself that needs to be unlinkable to the 
% voter, here the fact of having cast a vote at all needs to be unlinkable.

% The privacy properties we need in this context are the following:
% \begin{description}
%  \item[Involuntary participant unlinkability:] \daniel{the name has a 
%      double-negative ring to me} unless the participant discloses the receipt 
%    (by revealing her identity), there is no link between the protest data on 
%    the ledger and the identity of the participant.

%  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
%      too of course} unless the witness discloses the receipt (by revealing her 
%    identity), there is no link between the protest data on the ledger and the 
%    identity of the witness.
% \end{description}

% In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
% As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
% Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
% Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).

% As a consequence, this leaves us with with what would correspond to vote privacy.
% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
% \sonja{end older thoughts}
Moreover, any temporary identifiers such as pseudonyms may only be
reused when strictly necessary for the fulfillment of verifiability
properties listed in \label{verifiability-properties} to prevent
inference on long-term identities by repeated samples and side information.
